MADA Project Part 2

### 2024-02-23 R/processing-code/MADAproject_pt2_ruiz.qmd
Part 2
corrected typos

# Loading libraries
```{r, message=FALSE, warning=FALSE}
library(readxl) #for loading Excel files
library(httr)   #for getting data from the web
library(dplyr)  #for data processing/cleaning
library(tidyr)  #for data processing/cleaning
library(skimr)  #for visualizing data 
library(here)   #allows relative pathways for data
library(readr)
library(naniar) 
library(ggplot2)
library(sf)
library(topicmodels)
library(openxlsx)
library(lubridate)
library(knitr)
library(kableExtra)
library(webshot2)
library(magick)
library(leaflet)
library(htmlwidgets)
```
# Loading data

## Mosquito trap data
### This dataset contains trap counts by species for all mosquito traps set in the Bristol County from 2007-2023
```{r trap-data-import}
# Construct the path to the Excel file
file_path_mos <- here("data", "processed-data", "MOSQ_MADA.xlsx")

@@

#load the first few rows of data to verify the data loaded as expected
head(wx)
```
## Human and veterinary cases of eastern equine encephalitis and West Nile virus
```{r}
# Construct the path to the human case data file
file_path_human <- here("data", "processed-data", "human_cases.xlsx")

@@

#load the first few rows of data to verify the data loaded as expected
head(cases_vet)
```

>>>>

# Loading libraries
```{r, message=FALSE, warning=FALSE}
library(readxl) #for loading Excel files
library(httr)   #for getting data from the web
library(dplyr)  #for data processing/cleaning
library(tidyr)  #for data processing/cleaning
library(skimr)  #for visualizing data 
library(here)   #allows relative pathways for data
library(readr) #reading and writing data to and from CSV, TSV, and fixed-width files
library(naniar) #tools to work with missing data
library(ggplot2) #plot creation
library(sf) #standardized way to encode spatial data
library(topicmodels) #tools for topic modeling on text data
library(openxlsx) #Facilitates reading from and writing to .xlsx files
library(lubridate) #Simplifies the work with dates and times
library(knitr) #Allows for dynamic report generation in R
library(kableExtra) #generates simple HTML or LaTeX tables
library(webshot2) #tools to take screenshots of web pages 
library(magick) #advanced image processing in R
library(leaflet) #Enables the creation of interactive maps
library(htmlwidgets) #Facilitates the creation of R bindings to JavaScript libraries
```
# Loading data

## Mosquito trap data
### This dataset contains trap counts by species for all mosquito traps set in the Bristol County from 2007-2023
### this dataset will undergo extensive processing below. 
```{r trap-data-import}
# Construct the path to the Excel file
file_path_mos <- here("data", "processed-data", "MOSQ_MADA.xlsx")

@@

#load the first few rows of data to verify the data loaded as expected
head(wx)

#the columns below are the only ones needed for this project. 
wx_selected <- wx %>%
  select(STATION, NAME, DATE, PRCP)

head(wx_selected)
```
## Human and veterinary cases of eastern equine encephalitis and West Nile virus
```{r}
# Construct the path to the human case data file
file_path_human <- here("data", "processed-data", "human_cases.xlsx")

@@

#load the first few rows of data to verify the data loaded as expected
head(cases_vet)
#date of onset is missing for some records, however, they are not needed for this project.
